Concise Linkable Ring Signatures and Forgery Against Adversarial Keys

### 2020-07-03 paper/iacr.tex
Updated paper

\documentclass{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphics,graphicx}

\title{Arcturus: efficient proofs for confidential transactions}
\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
\date{\today}

\newcommand{\G}{\mathbb{G}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\hs}{\mathsf{H}}
\newcommand{\hp}{\mathcal{H}}
\newcommand{\com}{\operatorname{Com}}
\newcommand{\A}{\mathcal{A}}

\newcommand{\sumi}{\sum_{i=0}^{n-1}}
\newcommand{\sumj}{\sum_{j=0}^{m-1}}
\newcommand{\sumk}{\sum_{k=0}^{N-1}}
\newcommand{\sumu}{\sum_{u=0}^{w-1}}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\begin{document}

\maketitle

\begin{abstract}
Confidential transactions are used in distributed digital assets to demonstrate the balance of values hidden in commitments, while retaining signer ambiguity.
Previous work describes a signer-ambiguous proof of knowledge of the opening of commitments to zero at the same index across multiple public commitment sets and the evaluation of a verifiable random function used as a linking tag, and uses this to build a linkable ring signature called Triptych that can be used as a building block for a confidential transaction model.
In this work, we extend Triptych to build Arcturus, a proving system that proves knowledge of openings of multiple commitments to zero within a single set, correct construction of a verifiable random function evaluated at each opening, and value balance across a separate list of commitments within a single proof.
While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Arcturus can be used in a confidential transaction model to provide faster total batch verification time than other state-of-the-art constructions without a trusted setup.
\end{abstract}

\section{Introduction}
Distributed digital assets, starting with Bitcoin, rely on digital signatures to authorize transactions and transfer the spend authority of funds.
While early protocols based on the model established by Bitcoin have the advantage of simplicity, they lack desirable properties relating to privacy and indistinguishability.
In particular, the address and signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.

To protect users of distributed assets and permit better indistinguishability of transactions for fungibility, several methods have been proposed and deployed toward confidential transactions.
The CryptoNote protocol, an early proposal for obscuring transaction graphs, relies on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}; a transaction includes a separate signature for each such amount, yielding poor scaling.
A later advancement to the RingCT protocol \cite{ringct} used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} \cite{liu} to support parallel signatures in a matrix arrangement, removing the need for denominated transaction outputs altogether.
However, both of these constructions use linkable ring signatures that scale linearly in size with the size of the anonymity set used in each signature.

More recent methods of maintaining transaction privacy use accumulators to represent a given state of transaction outputs.
Zerocoin \cite{zerocoin} relied on RSA accumulators and associated proofs to assert the validity of transactions, but amounts were fixed, the protocol used very large and inefficient proofs, transactions were limited to a simple burn-mint operation on a transparent chain, and the use of RSA groups required a trusted setup process.
Later work produced Zerocash \cite{zerocash}, which replaced RSA accumulators and related proofs with succinct proofs relating to Merkle tree accumulators, enabling arbitrary amounts and direct anonymous transfers.
However, like Zerocoin, Zerocash used a proving system requiring a trusted setup process; this was eventually used as the basis for the Zcash protocols.

Until recently, transaction protocols desiring robust signer ambiguity and flexible direct anonymous transfers of arbitrary amounts faced a tradeoff between a trust-free construction and efficiency in proof sizes and verification complexity.
Recent work in this area generally relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
A one-of-many commitment-to-zero proving system of Groth and Kohlweiss \cite{groth} was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently by Bootle \cite{bootle}.
This proving system forms the basis of Lelantus \cite{lelantus}, which extends the Zerocoin-style transaction model of \cite{groth} by using multiple-base Pedersen commitments to incorporate amounts alongside serial numbers; a modification to the proofs shows balance, and multiple proofs are needed for typical transactions.
However, Lelantus transactions allow a transaction sender to later identify when the recipient spends their funds; a mitigation to this solves the tracing problem, but at the cost of eliminating a useful one-time addressing construction that ensures recipient anonymity.
The same proving system in \cite{groth} is used in Triptych \cite{triptych}, a multi-dimensional linkable ring signature construction that can be used to build confidential transactions similarly to \cite{ringct}; Triptych notably supports one-time addressing and arbitrary amounts, while still requiring the use of multiple proofs for transactions spending multiple transaction outputs.
Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and seems to result in larger proofs.

The Bulletproofs \cite{bulletproofs} proving system uses an inner-product compression method to build range and circuit satisfiability proofs with logarithmic size scaling.
Besides an increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to construct more specialized proving systems for confidential transactions.
Omniring \cite{omniring} uses this method to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
The result is very small proofs; however, verification is slower than other approaches, and requirements for unique group generators mean such proofs cannot be verified in efficient batches.
RingCT 3.0 \cite{rct3} also uses a Bulletproof-style construction.
In an early version, transactions required separate proofs for multiple inputs; while an update incorporates a single proof for all inputs to a transaction, it also requires that the number of inputs be padded to a power of two, which can yield poor verification complexity.

\subsection{Our contribution}
We extend the proving system in Triptych \cite{triptych} in two significant ways, which we call Arcturus.
First, we enable the prover to show knowledge of multiple signing keys in a single proof simultaneously using one set of combined proof elements; unlike \cite{rct3}, our modification admits any number of transaction inputs without limitations.
We retain the verifiable random function evaluation that produces linking tags, which are required for the detection of repeat signing with the same commitment opening across proofs.
Second, we show Pedersen commitment value balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
We note that the soundness of the resulting proving system depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.

Taken together, these changes have application to a transaction protocol for efficient use in blockchain confidential transactions that does not require any trusted setup process.
A transaction can sign for multiple signer-ambiguous inputs and prove that the transaction balances using a single proof, a major improvement to currently-deployed constructions that require multiple proofs and separate auxiliary Pedersen amount commitments.
Further, we use actual blockchain data from the Monero digital asset project to directly compare the overall size and verification time of Arcturus to that of Triptych and two separate RingCT 3.0 constructions.
We find that Arcturus provides superior verification performance compared to other trust-free confidential transaction constructions, with competitive size scaling.

\section{Preliminaries}
\subsection{Public parameters}
Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $\hs: \{0,1\}^* \to \F$ and $\hp: \{0,1\}^* \to \G$ be cryptographic hash functions.
Let $N = n^m$ be a positive integer, where $m > 1$ (for our construction, we will use $n = 2$).
Assume that $G$, $H$, $U$, and any point of the form $G_i$ or $H_i$ (possibly with multiple indices) are uniformly random generators of $\G$ whose discrete logarithm relationship to each other is unknown.
Note that all such generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
All such public parameters are assumed to comprise a global reference string known to all players; in particular, we generally exclude explicit reference to public parameters from algorithm definitions and Fiat-Shamir transcript hashes for readability.

\subsection{Tensor commitment}
Let $\com$ be an additively homomorphic commitment scheme that is perfectly hiding and (at least) computationally binding.
In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv rG + xH$ to be the commitment of the value $x$ with randomness $r$.

For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
$$\com(f,r) \equiv rG + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
using fixed independent generators as described above.

Operations on tensors are assumed to be performed componentwise; for example, if $f \equiv (f_{i,j,k})$ and $g \equiv (g_{i,j,k})$ are such tensors over $\F$, then $f + g \equiv (f_{i,j,k} + g_{i,j,k})$, and so forth.

\subsection{Other notation}
For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^{m-1} i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\subsection{Sigma protocols}
For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier it knows a witness corresponding to a statement in $\mathcal{R}$.

A sigma protocol is complete, sound, and zero-knowledge.
These definitions are well known and found, for example, in \cite{groth}.
Essentially, these properties are:
\begin{itemize}
\item \textit{Perfectly complete}: For a witness to a statement in $\mathcal{R}$, an honest prover always convinces an honest verifier of the validity.
\item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
\item \textit{Special honest-verifier zero knowledge}: Given a statement and known verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
\end{itemize}
Sigma protocols can be made non-interactive by replacing random verifier challenges with hash-based transcript challenges under the random oracle model; this approach is called the Fiat-Shamir heuristic \cite{fiat}.

\subsection{Hardness assumption}
We now define a novel cryptographic hardness assumption that is used later to show the soundness of our construction.

\begin{definition}[Dual-target discrete logarithm problem]
\label{def:dual}
Let $\G$ be a group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $n > 0$.
Consider the following game between a challenger and a probabilistic polynomial-time player $\A$:
\begin{itemize}
\item The challenger chooses $G,H \in \G$ uniformly at random and sends both to $\A$.
\item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
\item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
\end{itemize}
We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability at least $\epsilon$, the following are true:
\begin{itemize}
\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
\item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
\end{itemize}
\end{definition}

\section{Proving system}
We now present a sigma protocol for the following relation:
\begin{multline*}
\mathcal{R} \equiv \Bigg\{ \{M_i\}_{i=0}^{N-1},\{P_i\}_{i=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
This captures the necessary elements for transaction authorization, which we describe later; knowledge of signing keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction amounts balance.
Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between proofs.

Figures \ref{fig:sigma} and \ref{fig:sigma2} describe the prover and verifier interaction.
Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}:}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item For $0 \leq u < w$, define coefficients $\left\{p_{k,j}^{(u)}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k^{(u)}(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}^{(u)}x + a_{j,k}^{(u)} \right) = \delta\left(l^{(u)},k\right)x^m + \sumj p_{k,j}^{(u)}x^j$$ (using our decomposition notation).
Then define $p_{k,j} \equiv \sumu p_{k,j}^{(u)}$ and $p_k(x) \equiv \sumu p_k^{(u)}(x)$ accordingly.
\item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\},\{Z_j\}$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}$}
\label{fig:sigma}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f_{j,i}^{(u)} \equiv \sigma_{j,i}^{(u)}\xi + a_{j,i}^{(u)}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
\item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
\end{itemize}

>>>>

\documentclass{llncs}
\pagestyle{headings}

\usepackage{enumerate}
\usepackage{amsmath,amssymb}

\newcommand{\A}{\texttt{A}}
\newcommand{\B}{\texttt{B}}
\newcommand{\F}{\texttt{F}_p}
\newcommand{\G}{\texttt{G}}
\newcommand{\Hp}{\mathcal{H}^p}
\newcommand{\Hs}{\mathcal{H}^s}
\newcommand{\prob}{\mathbb{P}}

\title{Concise Linkable Ring Signatures and Forgery Against Adversarial Keys}
\institute{Monero Research Lab, \email{\{surae,sarang\}@getmonero.org} \and Independent researcher, \email{randomrun@protonmail.com}}
\author{Brandon Goodell\inst{1} \and Sarang Noether\inst{1} \and Arthur Blue\inst{2}}

\begin{document}
\maketitle

\begin{abstract}
We demonstrate that a version of non-slanderability is a natural definition of unforgeability for linkable ring signatures. We present a linkable ring signature construction with concise signatures and multi-dimensional keys that is linkably anonymous if a variation of the decisional Diffie-Hellman problem with random oracles is hard, linkable if key aggregation is a one-way function, and non-slanderable if a one-more variation of the discrete logarithm problem is hard. We remark on some applications in signer-ambiguous confidential transaction models without trusted setup.
\end{abstract}

\section{Introduction}

First introduced in \cite{rivest} in the RSA setting and in \cite{liu2004linkable} in the discrete logarithm setting, ring signatures permit message signing on behalf of a set of public keys rather than a single public key. Ring signatures see myriad applications ranging from lightweight anonymous authentication in \cite{yang2015lightweight} to transaction protocols like Monero in \cite{noether2016ring} and CryptoNote in \cite{van2013cryptonote}. A verifier is assured that the signer knows the private key of at least one of these public keys, which are called ring members. Ring signatures are anonymous or signer-ambiguous in the sense that the verifier does not learn information from the signature about which key is the signer. We stress that methods of practical analysis such as those of  \cite{moser2018empirical,quesnelle2017linkability} can exploit metadata in real-life applications of anonymous authentication protocols to reduce anonymity.

Group signature constructions preceding \cite{rivest,liu2004linkable} require some degree of interactivity, a fixed set of participants, a trusted group manager or other trusted setup, or hardness assumptions not based on the discrete logarithm problem. Since \cite{rivest}, ring signatures have enjoyed many improvements, extensions, and modifications. For example, ring signatures are constructed in the bilinear pairing setting in \cite{zhang2002id}, key structures are generalized in \cite{abe20021}, security definitions are improved in \cite{bender2006ring}, signature size is improved in \cite{fujisaki2011sub,gu2018constant}, and traceability is introduced in \cite{fujisaki2007traceable}.

Linkable ring signature (LRS) constructions were first introduced in \cite{liu2004linkable}; in the context of transaction protocols, linkable ring signatures are the basis for anonymous transaction authentication. Linkable ring signatures guarantee that two signatures with the same ring on arbitrary messages can be publicly linked if signed using the same key. An implementation is presented in \cite{liu2004linkable} in the discrete logarithm setting; that implementation functions for similar reasons as Schnorr signatures in \cite{schnorr1991efficient}.

The signature linking tags in \cite{liu2004linkable} are unsuitable for applications where signatures must be linked key-by-key, not ring-by-ring (such as for ``double-signing'' protection in a setting where users generate new keys over time and select \textit{ad hoc} ring members). Resistance to double-signing attempts is ensured using linking tags as described in \cite{van2013cryptonote} (therein called key images). More recent work of \cite{noether2016ring} extends the approach of \cite{liu2004linkable} to enable an anonymous confidential transaction model with \textit{ad hoc} ring member selection. In \cite{noether2016ring}, transaction amounts are replaced with Pedersen commitments to amounts together with range proofs. Signatures are constructed from key vectors including differences of amount commitments as one of the keys. However, the proofs in \cite{noether2016ring} are informal and not based on rigorous security models.

Alternatives to ring signatures like more general zero-knowledge proving systems typically require a trusted party to honestly perform a setup process (as in \cite{groth,ben2014succinct,groth2018updatable}) or lack practical efficiency for large circuits (as in \cite{bulletproofs}), meaning that such systems may not be appropriate for distributed ledger applications. However, more recent approaches such as \cite{hoffmann2019efficient} show both improvements to the trust requirement as well as improvements in efficiency.

Definitions of existential unforgeability for ring signature schemes from \cite{bender2006ring} are generally inappropriate for LRS. These definitions ensure that forgeries appear to be computed from uncorrupted challenge keys by restricting choices of anonymity set members and oracle queries. We can do better with linkability.

The idea of existential unforgeability in usual digital signatures is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature appears to be signed by an uncorrupted challenge key. The clear analogue for LRS schemes is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature links to a challenge signature computed from an uncorrupted challenge key.  Contrast this intuition with the definition of unforgeability for usual ring signatures with respect to insider corruption from \cite{bender2006ring}, which does not count a valid signature $\sigma$ with an anonymity set $Q$ as a forgery if any key in $Q$ is corrupt or not a challenge key, or a signing oracle has been queried with the same anonymity set $Q$ and message. This leads to two problems.

The first problem is due to the disqualification of a purported forgery if there are any adversarially-selected keys or corrupted challenge keys in the anonymity set. Such a signature that links with an uncorrupted challenge key does not count as a forgery. In ring signature schemes without linkability, this restriction seems requisite to ensure that the signature appears to be signed by an uncorrupted challenge key. In applications like signer-ambiguous transaction protocols that use anonymity sets selected \textit{ad hoc}, anonymity set members should be assumed to be adversarially generated. Definitions of unforgeability should take this into account.

The second problem is due to the signing oracle restriction in this definition. An adversary could generate a valid, non-oracle signature re-using the same message and anonymity set as some challenge signature generated by the oracle. A verifier who has found more than one valid non-oracle signature on the same message with the same anonymity set, under this definition, can only conclude that at least one anonymity set member signed at least one of the signatures. This allows a malicious Mallory-in-the-middle to collect outgoing honest signatures on some honest messages and attempt to construct clone signatures on these honest messages. A sender attempting to assert culpability over a signature could then be in danger of being unable to reconstruct a signature sent to some receiver.

These problems seem to interfere with the spirit behind existential unforgeability with insider corruption from \cite{bender2006ring}: the signature is valid, not produced by an oracle, appears to have been computed from an uncorrupted challenge key, and yet is not considered a forgery.

\subsection{Our Contribution}

We relax the notion of successful forgeries to require only linking with uncorrupted challenge keys, obtaining a notion of unforgeability for linkable ring signatures that is equivalent to the definition of non-slanderability in \cite{au2006short}.  Non-slanderability allows for adversaries who can query a signature oracle with any anonymity set, even adversarially-selected anonymity sets. This models an extremely persuasive adversary who can convince users to sign messages with adversarially-selected anonymity sets. We show that non-slanderability implies unforgeability with respect to insider corruption from \cite{bender2006ring}.

We also present a Schnorr-like linkable ring signature scheme we call $d$-CLSAG that exploits key aggregation techniques to improve signature size. We describe an application for the $d$-CLSAG scheme in ring confidential transaction protocols, allowing transactions consisting of $d-1$ distinct assets simultaneously. We prove that $d$-CLSAG is linkable assuming collision resistance in key aggregation and linkably anonymous assuming a variant of the decisional Diffie-Hellman game is hard. Recall that Schnorr-like signature schemes do not cleanly reduce to the discrete logarithm assumption (\textit{c.f.}\ \cite{paillier2005discrete}), generally are only secure up to the (relatively flimsier) one-more hardness assumptions, and proof techniques typically exploit programmable random oracles with forking lemmata, leading to weak bounds. We use the general forking lemma to prove that $d$-CLSAG is non-slanderable assuming a $\kappa$-one-more variation of the discrete logarithm game is hard.

\section{Preliminaries}

Let $\lambda$ be a security parameter and $1 \leq q, \eta, \kappa \in poly(\lambda)$. Let $\G = \langle G \rangle$ denote a finite cyclic group over a finite field $\F$ for some prime $p$, with group generator $G$.  Let $\Hs:\left\{0,1\right\}^* \to \F$ and $\Hp:\left\{0,1\right\}^* \to \G$ be two independent cryptographic hash functions modeled as random oracles.

If there exists a function $f$ that is negligible in some parameter $\lambda$, and there exists $\lambda$-dependent events $A, B$ such that $\left|\prob\left[A\right] - \prob\left[B\right]\right| \leq f(\lambda)$, we denote this $\prob\left[A\right] \approx \prob\left[B\right]$. An event $A$ such that $\prob\left[A\right] \approx 0$ is said to be negligible in $\lambda$ (or to occur with probability at most negligible in $\lambda$). The complement of an event $A$ is denoted $\overline{A}$. For the field $\F$, we denote the non-zero elements $\F^* := \F\setminus \left\{0\right\}$. For a finite set $S$, we define $S^*$ by interpreting $S$ as a list of letters that generate the free monoid $S^*$. For example, $\left\{0,1\right\}^*$ consists of all finite-length bitstrings.

For a set $S$, we define $\mathcal{P}(S)$ as the power set of $S$, i.e.\ the set of all subsets of $S$.

We denote vectors with bold, i.e.\ for a sequence $x_i \in \F$ for $i = 0, \ldots, n-1$, we denote the tuple $(x_0, \ldots, x_{n-1})$ with $\textbf{x}$. We denote the Hadamard product between vectors with $\textbf{x} \circ \textbf{y} = (x_i y_i)_i$. We begin all indices at $0$ to avoid all ambiguity. We use the notation $[n]$ to mean the set $\{0,\ldots,n-1\}$.

\section{Definitions}

\subsection{Hardness Assumptions}\label{sec:hardness}

We begin by noting that if $\left\{\mu_i: \F^d \to \F\right\}_{i=0}^{d-1}$ are functions selected uniformly at random, then the composite function $\mu: \F^d \to \F$ defined by mapping $\textbf{x} \mapsto \sum_i \mu_i(\textbf{x}) x_i$ has uniformly distributed output and is a collision- and preimage-resistant function. We use this property later when considering linkability and linkable anonymity.

The following game is equivalent\footnote{A usual $\kappa$-one-more discrete logarithm solver can succeed at the game in Definition \ref{def:komdl} with the same probability and some extra time by merely summing solutions. A solver of the game in Definition \ref{def:komdl} can use their discrete logarithm knowledge to solve for an otherwise uncorrupted challenge key with the same probability and some extra time.} to the usual $\kappa$-one-more discrete logarithm game under the random oracle model.

\begin{definition}[$\kappa$-One-More Linear Combination Discrete Logarithm]\label{def:komdl}

Let $\kappa \geq 1$. We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the $\kappa$-one-more discrete logarithm of linear combinations problem in $\G$ (where $k < q$).
\begin{enumerate}
\item Challenger draws $\left\{sk_i\right\}_{i=0}^{q-1} \subseteq \F$ at random, computes $pk_i := sk_i \cdot G$, sends $S := \left\{pk_i\right\}_{i=0}^{q-1}$ to $\A$.

\item $\A$ is granted access to a corruption oracle $\texttt{CO}$ which takes as input a public key $pk_i \in S$ and produces as output the corresponding private key $sk_i$. Corrupted keys are recorded in a table $C$.

\item $\A$ outputs some $w \in \F^*$, a sequence of field elements $\left\{h_j\right\}_{j=0}^{\kappa} \subseteq \F \setminus \left\{0\right\}$, and a subset of challenger keys $\left\{pk^*_j\right\}_{j=0}^{\kappa} \subseteq \left\{pk_i\right\}_{i=0}^{q-1}$, succeeding if and only if $w \cdot G = \sum_{j=0}^{\kappa} h_j \cdot pk^*_j$ and
 $\A$ queried $\texttt{CO}$ no more than $\kappa$ times.

\end{enumerate}
We say that the discrete logarithms of linear combinations are computationally hard to compute in $\G$ if any $(t, \epsilon, q)$-solver of this game has an advantage  that is $\epsilon$ negligible in $q$.
\end{definition}

For an algorithm $\A$ that takes as input a random tape $\rho$, a sequence of random oracle queries $\textbf{h}$ and some input $inp$ and produces $(out, idx) \leftarrow \A(\rho, \textbf{h}, inp)$ as output, the general forking algorithm works as follows.

\begin{enumerate}[(1)]
\item  Pick a random tape $\rho$ for $\A$ and two sequences of random oracle queries $\textbf{h} = \left\{h_0, h_1, \ldots\right\}$ and $\textbf{h}^\prime = \left\{h_0^\prime, h_1^\prime, \ldots\right\}$.

\item Execute $(out, idx) \leftarrow \A(\rho, \textbf{h}, inp)$.

\item Set $j := idx$ and glue the oracle queries $\textbf{h}$, $\textbf{h}^\prime$ together \[\textbf{h}^* = \left\{h_0, h_1, \ldots, h_{idx - 1}, h_{idx}^\prime, h_{idx+1}^\prime, \ldots, \right\}.\]

\item Execute $(out^*, idx^*) \leftarrow \A(\rho, \textbf{h}^*, inp)$.

\item If $idx \neq idx^*$ or $h_{idx} = h_{idx}^\prime$, output $\bot$ and terminate. Otherwise, output $(out, out^\prime, idx)$.
\end{enumerate}

This algorithm is precisely the algorithm $\mathcal{F}^{\A}$ in the following lemma.

\begin{lemma}[General Forking Lemma]\label{lem:fork}
Let $1 \leq \eta \in \text{poly}(\lambda)$. Let $\A$ be any PPT algorithm which takes as input some tuple $x_\A = (x, \textbf{h})$ where we let $\textbf{h} = (h_0, h_1, \ldots, h_{q-1})$ be a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\A}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output. Let $\epsilon_{\A}$ denote the probability that $\A$ does not output $\bot_{\A}$ (where this probability is taken over all random coins of $\A$, the distribution of $x$, and all choices $\textbf{h}$). Let $\mathcal{F} = \mathcal{F}^{\A}$ be a forking algorithm for $\A$. The accepting probability of $\mathcal{F}$ satisfies $\epsilon_{\mathcal{F}} \geq \epsilon_{\A} \left(\frac{\epsilon_{\A}}{q} - \frac{1}{2^\eta}\right)$.
\end{lemma}

We use the next game to relate the classic decisional Diffie-Hellman hardness assumption to a random oracle construction that will be useful later when introducing a definition of linkable anonymity. Detailed properties of this type of construction relating to pseudorandomness and invertibility are formalized and discussed further in \cite{omniring}.

\begin{definition}[Random Oracle Decisional Diffie-Hellman]\label{def:rom-ddh}
We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ with advantage least $\epsilon > 0$ over random chance is a $(t,\epsilon,q)$-solver of the random oracle decisional Diffie-Hellman game.
\begin{itemize}
\item The challenger chooses a bit $b \in \{0,1\}$ uniformly at random.
\item If $b = 0$, then the challenger chooses $\{r_i\}_{i=0}^{q-1}$ from $\F$ uniformly at random, sets $$S := \{(R_i,R_i',R_i'')\}_{i=0}^{q-1} = \{(r_iG,\Hp(r_iG),r_i\Hp(r_iG))\}_{i=0}^{q-1},$$ and sends $S$ to $\A$.
\item If instead $b = 1$, then the challenger chooses $\{(r_i,r_i'')\}_{i=0}^{q-1}$ from $\F^2$ uniformly at random, sets $$S := \{(R_i,R_i',R_i'')\}_{i=0}^{q-1} = \{(r_iG,\Hp(r_iG),r_i''G)\}_{i=0}^{q-1},$$ and sends $S$ to $\A$.
\item $\A$ is granted access to the random oracle $\Hp$.
\item $\A$ returns a bit $b' \in \{0,1\}$; we say $\A$ succeeds if and only if $b' = b$.
\end{itemize}
We say that random oracle Diffie-Hellman group elements are hard to distinguish from random in $\G$ if any $(t,\epsilon,q)$-solver of this game has negligible advantage $\epsilon$.
\end{definition}

\begin{remark}
We assume that if the classic decisional Diffie-Hellman (DDH) game is hard in $\G$, then so is the RO-DDH game. Indeed, recall that DDH asks an adversary to distinguish between distributions of tuples of the form $(rG,r'G,rr'G)$ and $(rG,r'G,r''G)$. If DDH is hard in $\G$, then distributions of tuples of these forms are indistinguishable. Since $\Hp$ is a random oracle whose output is independent of input, then distributions of tuples of the form $(rG,\Hp(rG),r''G)$ and $(rG,r'G,r''G)$ are identical. Similarly, distributions of tuples of the form $(rG,\Hp(rG),r\Hp(rG))$ and $(rG,\Hp(rG),r''G)$ are identical. Finally, random self-reducibility of the classic DDH game means that solving one instance of the problem has complexity no worse than solving a sequence of random instances of the problem.
\end{remark}

\subsection{Linkable Ring Signatures}

\begin{definition}\label{def:lrs} A linkable ring signature (LRS) scheme $\Pi_{LRS}$ is a tuple of PPT algorithms $(\texttt{SETUP}, \texttt{KEYGEN}, \texttt{SIGN}, \texttt{VERIFY}, \texttt{LINK})$ satisfying the following set of constraints:
\begin{itemize}
\item $\texttt{SETUP}$ takes as input a security parameter $\lambda$ and produces as output some public setup parameters $\rho$.

\item $\texttt{KEYGEN}$ is a randomized; it takes as input $(\lambda, \rho)$ and outputs a private-public keypair $(sk, pk)$.
